---
title: "DinuralCycles"
author: "Juliana Cerny"
date: '2023-02-05'
output: html_document
---

# use summer2022.csv, fall2022.csv

load data and change variable names 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
library(tidyr)
library(reshape2)
library(lubridate)
library(ggpubr)
library(RColorBrewer)
library(naniar)

summer2022<-read.csv("C:/Users/julia/OneDrive/Documents/Morven/Diurnal Cycles/summer2022.csv")

summer2022<-rename(summer2022,
                   A.airtemp="Temperature..RXW.THC.20778368.20779618.1....F..UVA.ARC.1",
                   A.windspeed= "Wind.Speed..RXW.WCF.20778368.20735930.1...mph..UVA.ARC.1",
                   A.winddirection="Wind.Direction..RXW.WCF.20778368.20735930.3......UVA.ARC.1",
                   B.soilmoist="Water.Content..S.SMC.20778368.20773519.1...m.3.m.3..UVA.ARC.1",
                   B.soiltemp="Temperature..S.TMB.20778368.20770097.1....F..UVA.ARC.1",
                   B.airtemp="Temperature..S.THB.20778368.20777744.1....F..UVA.ARC.1",
                   B.rad="Solar.Radiation..S.LIB.20778368.20779676.1...W.m.2..UVA.ARC.1",
                   B.windspeed="Wind.Speed..S.WSB.20778368.20779920.1...mph..UVA.ARC.1",
                   B.winddirection="Wind.Direction..S.WDA.20778368.20774023.1......UVA.ARC.1",
                   C.airtemp="Temperature..RXW.THC.20778368.20780856.1....F..UVA.ARC.1",
                   C.windspeed="Wind.Speed..RXW.WCF.20778368.20735931.1...mph..UVA.ARC.1",
                   C.winddirection="Wind.Direction..RXW.WCF.20778368.20735931.3......UVA.ARC.1",
                   D.airtemp="Temperature..RXW.THC.20778368.20778336.1....F..UVA.ARC.1",
                   D.windspeed="Wind.Speed..RXW.WCF.20778368.20779630.1...mph..UVA.ARC.1",
                   D.winddirection="Wind.Direction..RXW.WCF.20778368.20779630.3......UVA.ARC.1",
                   D.rad="Solar.Radiation..RXW.LIB.20778368.20735864.1...W.m.2..UVA.ARC.1.SR_E6",
                   F.airtemp="Temperature..RXW.THC.20778368.20778338.1....F..UVA.ARC.1",
                   E.soiltemp="Temperature..RXW.TMB.20778368.20776843.1....F..UVA.ARC.1",
                   E.airtemp="Temperature..RXW.THC.20778368.20780852.1....F..UVA.ARC.1",
                   E.rad="Solar.Radiation..RXW.LIB.20778368.20748041.1...W.m.2..UVA.ARC.1.SR_G6",
                   E.windspeed="Wind.Speed..RXW.WCF.20778368.20779625.1...mph..UVA.ARC.1",
                   E.winddirection="Wind.Direction..RXW.WCF.20778368.20779625.3......UVA.ARC.1",
                   F.windspeed="Wind.Speed..RXW.WCF.20778368.20779627.1...mph..UVA.ARC.1",
                   F.winddirection="Wind.Direction..RXW.WCF.20778368.20779627.3......UVA.ARC.1",
                   F.rad="Solar.Radiation..RXW.LIB.20778368.20779612.1...W.m.2..UVA.ARC.1",
                   G.airtemp="Temperature..RXW.THC.20778368.20779619.1....F..UVA.ARC.1",
                   G.windspeed="Wind.Speed..RXW.WCF.20778368.20779626.1...mph..UVA.ARC.1",
                   G.winddirection="Wind.Direction..RXW.WCF.20778368.20779626.3......UVA.ARC.1",
                   G.rad="Solar.Radiation..RXW.LIB.20778368.20735865.1...W.m.2..UVA.ARC.1.SR_G5",
                   N.airtemp="Temperature..RXW.THC.20778368.20780854.1....F..UVA.ARC.1",
                   N.windspeed="Wind.Speed..RXW.WCF.20778368.20779624.1...mph..UVA.ARC.1",
                   N.winddirection="Wind.Direction..RXW.WCF.20778368.20779624.3......UVA.ARC.1",
                   N.rad="Solar.Radiation..RXW.LIB.20778368.20735863.1...W.m.2..UVA.ARC.1.SR_B4")
```



converting all variables to numeric and removing commas from radiation vectors
```{r}
summer2022$Date<-as.POSIXct(summer2022$Date,format="%m/%d/%Y %H",tz="UTC")

summer2022$B.rad<-as.numeric(gsub(",","",summer2022$B.rad))
summer2022$D.rad<-as.numeric(gsub(",","",summer2022$D.rad))
summer2022$E.rad<-as.numeric(gsub(",","",summer2022$E.rad))
summer2022$F.rad<-as.numeric(gsub(",","",summer2022$F.rad))
summer2022$G.rad<-as.numeric(gsub(",","",summer2022$G.rad))
summer2022$N.rad<-as.numeric(gsub(",","",summer2022$N.rad))

summer2022$B.rad<-as.numeric(summer2022$B.rad)
summer2022$D.rad<-as.numeric(summer2022$D.rad)
summer2022$E.rad<-as.numeric(summer2022$E.rad)
summer2022$F.rad<-as.numeric(summer2022$F.rad)
summer2022$G.rad<-as.numeric(summer2022$G.rad)
summer2022$N.rad<-as.numeric(summer2022$N.rad)
```


separate variables into new dataframes
```{r}
Airtemp<-summer2022[ , c("Date","A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp")]

Radiation<-summer2022[ , c("Date","B.rad","D.rad","E.rad","F.rad","G.rad","N.rad")]%>%
  replace_with_na(replace=list(D.rad=-888.88))
```



plot theme
```{r}
theme_xangle<-theme_bw() + 
  theme(title = element_text(size=20),
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust=1))

theme1<-theme_bw()+
  theme(title = element_text(size=20),
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        axis.text.x = element_text( vjust = 1, hjust=1))
```


### Air temp by hour over a week - june-aug 2022
```{r fig1, fig.height=8, fig.width=20}
png("C:/Users/julia/OneDrive/Documents/Morven/Diurnal Cycles/Plots/Airtemp.diurnal.summer2022.png",width=800,height=400)

Airtemp<-summer2022[ , c("Date","A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp")]

Airtemp.hourly.means<-Airtemp%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  mutate(Day=as.Date(Date))%>%
  mutate(Hour=format(as.POSIXct(Date),format="%H"))%>%
  group_by(Hour) %>%
  mutate(SD = sd(na.omit(unlist(select(cur_data(), 3:9)))))%>%
  mutate(Mean= mean(na.omit(unlist(select(cur_data(), 3:9)))))%>%
  summarise_if(is.numeric, mean)

Airtemp.hourly.means.long<-Airtemp.hourly.means%>%pivot_longer(cols=c("B.airtemp","C.airtemp","D.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp","Mean"),names_to="Sensor",values_to="value")

ggplot()+
  geom_line(data=Airtemp.hourly.means,aes(x=Hour,y=Mean,group=1),color="darkgrey",size=2)+
  geom_point(data=Airtemp.hourly.means.long,aes(x=Hour,y=value,color=Sensor))+
  geom_line(data=Airtemp.hourly.means.long,aes(x=Hour,y=value,color=Sensor,group=Sensor))+
  labs(title="ARC 1 Mean Hourly Air Temperature (F) June 1 - Aug 31, 2022",x="24 Hour Cycle",y="Air Temperature (deg F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B.airtemp"="gold1","C.airtemp"="red","D.airtemp"="darkorchid3","E.airtemp"="navy","F.airtemp"="maroon","G.airtemp"="limegreen","N.airtemp"="darkgreen"))+
  theme1

dev.off()
```

### Air temp by hour over a week - june 17-24 2022
```{r fig1, fig.height=8, fig.width=20}
png("C:/Users/julia/OneDrive/Documents/Morven/Diurnal Cycles/Plots/Airtemp.diurnal.jun17_14_2022.png",width=800,height=400)

Airtemp<-summer2022[ , c("Date","A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp")]%>%
   filter(Date > "2022-06-17 00:00:00" & Date <"2022-06-24 23:55:00")


Airtemp.hourly.means<-Airtemp%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  mutate(Day=as.Date(Date))%>%
  mutate(Hour=format(as.POSIXct(Date),format="%H"))%>%
  group_by(Hour) %>%
  mutate(SD = sd(na.omit(unlist(select(cur_data(), 3:9)))))%>%
  mutate(Mean= mean(na.omit(unlist(select(cur_data(), 3:9)))))%>%
  summarise_if(is.numeric, mean)

Airtemp.hourly.means.long<-Airtemp.hourly.means%>%pivot_longer(cols=c("B.airtemp","C.airtemp","D.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp","Mean"),names_to="Sensor",values_to="value")

ggplot()+
  geom_line(data=Airtemp.hourly.means,aes(x=Hour,y=Mean,group=1),color="darkgrey",size=2)+
  geom_point(data=Airtemp.hourly.means.long,aes(x=Hour,y=value,color=Sensor))+
  geom_line(data=Airtemp.hourly.means.long,aes(x=Hour,y=value,color=Sensor,group=Sensor))+
  labs(title="ARC 1 Mean Hourly Air Temperature (F) June 17-24, 2022",x="24 Hour Cycle",y="Air Temperature (deg F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B.airtemp"="gold1","C.airtemp"="red","D.airtemp"="darkorchid3","E.airtemp"="navy","F.airtemp"="maroon","G.airtemp"="limegreen","N.airtemp"="darkgreen"))+
  theme1

dev.off()
```

### Radiation by hour over a week - june-aug 2022
```{r fig1, fig.height=8, fig.width=20}
png("C:/Users/julia/OneDrive/Documents/Morven/Diurnal Cycles/Plots/Radiation.diurnal.summer2022.png",width=800,height=400)

# remove A,c,D
Radiation<-summer2022[ , c("Date","B.rad","E.rad","F.rad","G.rad","N.rad")]

Rad.hourly.means<-Radiation%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  mutate(Day=as.Date(Date))%>%
  mutate(Hour=format(as.POSIXct(Date),format="%H"))%>%
  group_by(Hour)%>%
  mutate(SD = sd(na.omit(unlist(select(cur_data(), 2:6)))))%>%
  mutate(Mean= mean(na.omit(unlist(select(cur_data(), 2:6)))))%>%
  summarise_if(is.numeric, mean)

Rad.hourly.means.long<-Rad.hourly.means%>%
  pivot_longer(cols=c("B.rad","E.rad","F.rad","G.rad","N.rad","Mean"),names_to="Sensor",values_to="value")

ggplot()+
  geom_line(data=Rad.hourly.means,aes(x=Hour,y=Mean,group=1),color="darkgrey",size=2)+
  geom_point(data=Rad.hourly.means.long,aes(x=Hour,y=value,color=Sensor))+
  geom_line(data=Rad.hourly.means.long,aes(x=Hour,y=value,color=Sensor,group=Sensor))+
  labs(title="ARC 1 Mean Hourly Air Temperature (F) June 1 - Aug 31, 2022",x="24 Hour Cycle",y="Air Temperature (deg F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B.rad"="gold1","C.rad"="red","D.rad"="darkorchid3","E.rad"="navy","F.rad"="maroon","G.rad"="limegreen","N.rad"="darkgreen"))+
  theme1

dev.off()
```


### Radiation by hour over a week - june 17-24 2022
```{r fig1, fig.height=8, fig.width=20}
png("C:/Users/julia/OneDrive/Documents/Morven/Diurnal Cycles/Plots/Radiation.diurnal.jun17_14_2022.png",width=800,height=400)

# remove A,c,D
Radiation<-summer2022[ , c("Date","B.rad","E.rad","F.rad","G.rad","N.rad")]%>%
   filter(Date > "2022-06-17 00:00:00" & Date <"2022-06-24 23:55:00")

Rad.hourly.means<-Radiation%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  mutate(Day=as.Date(Date))%>%
  mutate(Hour=format(as.POSIXct(Date),format="%H"))%>%
  group_by(Hour)%>%
  mutate(SD = sd(na.omit(unlist(select(cur_data(), 2:6)))))%>%
  mutate(Mean= mean(na.omit(unlist(select(cur_data(), 2:6)))))%>%
  summarise_if(is.numeric, mean)

Rad.hourly.means.long<-Rad.hourly.means%>%
  pivot_longer(cols=c("B.rad","E.rad","F.rad","G.rad","N.rad","Mean"),names_to="Sensor",values_to="value")

ggplot()+
  geom_line(data=Rad.hourly.means,aes(x=Hour,y=Mean,group=1),color="darkgrey",size=2)+
  geom_point(data=Rad.hourly.means.long,aes(x=Hour,y=value,color=Sensor))+
  geom_line(data=Rad.hourly.means.long,aes(x=Hour,y=value,color=Sensor,group=Sensor))+
  labs(title="ARC 1 Mean Hourly Air Temperature (F) June 17-24, 2022",x="24 Hour Cycle",y="Air Temperature (deg F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B.rad"="gold1","C.rad"="red","D.rad"="darkorchid3","E.rad"="navy","F.rad"="maroon","G.rad"="limegreen","N.rad"="darkgreen"))+
  theme1

dev.off()
```


Radiation Hourly Means 6/19/2022 - 6/24/2022
```{r}
Radiation<-summer2022[ , c("Date","B.rad","D.rad","E.rad","F.rad","G.rad","N.rad")]%>%
  replace_with_na(replace=list(D.rad=-888.88))


Radiation.hourly.means<-Radiation%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  group_by(Date) %>%
  summarise_if(is.numeric, mean)

Radiation.hourly.sd<-Radiation%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  group_by(Date) %>%
  mutate(SD = sd(na.omit(unlist(select(cur_data(), 1:6)))))%>%
  mutate(Mean= mean(na.omit(unlist(select(cur_data(), 1:6)))))%>%
  summarise_if(is.numeric, mean)

datebreaks<-seq.POSIXt(as.POSIXct("2022-06-19 00:00:00"),as.POSIXct("2022-06-24 23:00:00"),by="12 hours")

Radiation.hourly.means<-melt(Radiation.hourly.means,id.vars="Date",variable.name="Sensor")

ggplot()+
  geom_line(data=Radiation.hourly.means, aes(Date,value,group=Sensor),color="gray")+
  geom_point(data=Radiation.hourly.means, aes(Date,value,group=Sensor),color="gray")+
  geom_errorbar(data=Radiation.hourly.sd, aes(x=Date,ymin=Mean-SD, ymax=Mean+SD),  position=position_dodge(.9))+
  geom_point(data=Radiation.hourly.sd, aes(x=Date,y=Mean))+
  scale_x_datetime(breaks=datebreaks)+
  xlim(as.POSIXct("2022-06-19 00:00:00"),as.POSIXct("2022-06-24 23:00:00"))+
  labs(title="ARC 1 Hourly Solar Radiation (W/m^2) June 19-24, 2022",x="Date",y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  theme_xangle

```



Radiation Hourly Means June-July
```{r}
Radiation<-summer2022[ , c("Date","B.rad","D.rad","E.rad","F.rad","G.rad","N.rad")]%>%
  replace_with_na(replace=list(D.rad=-888.88))


Radiation.hourly.means<-Radiation%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  group_by(Date) %>%
  summarise_if(is.numeric, mean)

Radiation.hourly.sd<-Radiation%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  group_by(Date) %>%
  mutate(SD = sd(na.omit(unlist(select(cur_data(), 1:6)))))%>%
  mutate(Mean= mean(na.omit(unlist(select(cur_data(), 1:6)))))%>%
  summarise_if(is.numeric, mean)

datebreaks<-seq.POSIXt(as.POSIXct("2022-06-01 00:00:00"),as.POSIXct("2022-07-31 23:00:00"),by="2 days")

Radiation.hourly.means<-melt(Radiation.hourly.means,id.vars="Date",variable.name="Sensor")

ggplot()+
  geom_line(data=Radiation.hourly.means, aes(Date,value,group=Sensor),color="gray")+
  geom_point(data=Radiation.hourly.means, aes(Date,value,group=Sensor),color="gray")+
  geom_errorbar(data=Radiation.hourly.sd, aes(x=Date,ymin=Mean-SD, ymax=Mean+SD),  position=position_dodge(.9))+
  geom_point(data=Radiation.hourly.sd, aes(x=Date,y=Mean))+
  scale_x_datetime(breaks=datebreaks)+
  xlim(as.POSIXct("2022-06-01 00:00:00"),as.POSIXct("2022-07-31 23:00:00"))+
  labs(title="ARC 1 Hourly Solar Radiation (W/m^2) Summer, 2022",x="Date",y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  theme_xangle

```



########################################################################################

### Fall Data
```{r}

fall2022<-read.csv("C:/Users/julia/OneDrive/Documents/Morven/Diurnal Cycles/fall2022.csv")

fall2022<-rename(fall2022,
                   A.airtemp="Temperature..RXW.THC.20778368.20779618.1....F..UVA.ARC.1",
                   B.airtemp="Temperature..S.THB.20778368.20777744.1....F..UVA.ARC.1",
                   B.rad="Solar.Radiation..S.LIB.20778368.20779676.1...W.m.2..UVA.ARC.1",
                   C.airtemp="Temperature..RXW.THC.20778368.20780856.1....F..UVA.ARC.1",
                   D.airtemp="Temperature..RXW.THC.20778368.20778336.1....F..UVA.ARC.1",
                   D.rad="Solar.Radiation..RXW.LIB.20778368.20735864.1...W.m.2..UVA.ARC.1.SR_E6",
                   F.airtemp="Temperature..RXW.THC.20778368.20778338.1....F..UVA.ARC.1",
                   E.airtemp="Temperature..RXW.THC.20778368.20780852.1....F..UVA.ARC.1",
                   E.rad="Solar.Radiation..RXW.LIB.20778368.20748041.1...W.m.2..UVA.ARC.1.SR_G6",
                   F.rad="Solar.Radiation..RXW.LIB.20778368.20779612.1...W.m.2..UVA.ARC.1",
                   G.airtemp="Temperature..RXW.THC.20778368.20779619.1....F..UVA.ARC.1",
                   G.rad="Solar.Radiation..RXW.LIB.20778368.20735865.1...W.m.2..UVA.ARC.1.SR_G5",
                   N.airtemp="Temperature..RXW.THC.20778368.20780854.1....F..UVA.ARC.1",
                   N.rad="Solar.Radiation..RXW.LIB.20778368.20735863.1...W.m.2..UVA.ARC.1.SR_B4")
```




converting all variables to numeric and removing commas from radiation vectors
```{r}
fall2022$Date<-as.POSIXct(fall2022$Date,format="%m/%d/%Y %H",tz="UTC")

fall2022$B.rad<-as.numeric(gsub(",","",fall2022$B.rad))
fall2022$D.rad<-as.numeric(gsub(",","",fall2022$D.rad))
fall2022$E.rad<-as.numeric(gsub(",","",fall2022$E.rad))
fall2022$F.rad<-as.numeric(gsub(",","",fall2022$F.rad))
fall2022$G.rad<-as.numeric(gsub(",","",fall2022$G.rad))
fall2022$N.rad<-as.numeric(gsub(",","",fall2022$N.rad))

fall2022$B.rad<-as.numeric(fall2022$B.rad)
fall2022$D.rad<-as.numeric(fall2022$D.rad)
fall2022$E.rad<-as.numeric(fall2022$E.rad)
fall2022$F.rad<-as.numeric(fall2022$F.rad)
fall2022$G.rad<-as.numeric(fall2022$G.rad)
fall2022$N.rad<-as.numeric(fall2022$N.rad)
```


separate variables into new dataframes
```{r}
Airtemp<-fall2022[ , c("Date","A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp")]

Radiation<-fall2022[ , c("Date","B.rad","D.rad","E.rad","F.rad","G.rad","N.rad")]%>%
  replace_with_na(replace=list(D.rad=-888.88))
```


### Air temp by hour over a week - Sept-Nov 2022
```{r fig1, fig.height=8, fig.width=20}
png("C:/Users/julia/OneDrive/Documents/Morven/Diurnal Cycles/Plots/Airtemp.diurnal.fall2022.png",width=800,height=400)

Airtemp<-fall2022[ , c("Date","A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp")]

Airtemp.hourly.means<-Airtemp%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  mutate(Day=as.Date(Date))%>%
  mutate(Hour=format(as.POSIXct(Date),format="%H"))%>%
  group_by(Hour) %>%
  mutate(SD = sd(na.omit(unlist(select(cur_data(), 3:9)))))%>%
  mutate(Mean= mean(na.omit(unlist(select(cur_data(), 3:9)))))%>%
  summarise_if(is.numeric, mean)

Airtemp.hourly.means.long<-Airtemp.hourly.means%>%pivot_longer(cols=c("B.airtemp","C.airtemp","D.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp","Mean"),names_to="Sensor",values_to="value")

ggplot()+
  geom_line(data=Airtemp.hourly.means,aes(x=Hour,y=Mean,group=1),color="darkgrey",size=2)+
  geom_point(data=Airtemp.hourly.means.long,aes(x=Hour,y=value,color=Sensor))+
  geom_line(data=Airtemp.hourly.means.long,aes(x=Hour,y=value,color=Sensor,group=Sensor))+
  labs(title="ARC 1 Mean Hourly Air Temperature (F) Sept 1 - Nov 31, 2022",x="24 Hour Cycle",y="Air Temperature (deg F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B.airtemp"="gold1","C.airtemp"="red","D.airtemp"="darkorchid3","E.airtemp"="navy","F.airtemp"="maroon","G.airtemp"="limegreen","N.airtemp"="darkgreen"))+
  theme1

dev.off()
```

### Air temp by hour over a week - Oct 17-24 2022
```{r fig1, fig.height=8, fig.width=20}
png("C:/Users/julia/OneDrive/Documents/Morven/Diurnal Cycles/Plots/Airtemp.diurnal.Oct17_24_2022.png",width=800,height=400)

Airtemp<-fall2022[ , c("Date","A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp")]%>%
   filter(Date > "2022-10-17 00:00:00" & Date <"2022-10-24 23:55:00")


Airtemp.hourly.means<-Airtemp%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  mutate(Day=as.Date(Date))%>%
  mutate(Hour=format(as.POSIXct(Date),format="%H"))%>%
  group_by(Hour) %>%
  mutate(SD = sd(na.omit(unlist(select(cur_data(), 3:9)))))%>%
  mutate(Mean= mean(na.omit(unlist(select(cur_data(), 3:9)))))%>%
  summarise_if(is.numeric, mean)

Airtemp.hourly.means.long<-Airtemp.hourly.means%>%pivot_longer(cols=c("B.airtemp","C.airtemp","D.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp","Mean"),names_to="Sensor",values_to="value")

ggplot()+
  geom_line(data=Airtemp.hourly.means,aes(x=Hour,y=Mean,group=1),color="darkgrey",size=2)+
  geom_point(data=Airtemp.hourly.means.long,aes(x=Hour,y=value,color=Sensor))+
  geom_line(data=Airtemp.hourly.means.long,aes(x=Hour,y=value,color=Sensor,group=Sensor))+
  labs(title="ARC 1 Mean Hourly Air Temperature (F) October 17-24, 2022",x="24 Hour Cycle",y="Air Temperature (deg F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B.airtemp"="gold1","C.airtemp"="red","D.airtemp"="darkorchid3","E.airtemp"="navy","F.airtemp"="maroon","G.airtemp"="limegreen","N.airtemp"="darkgreen"))+
  theme1

dev.off()
```

### Radiation by hour over a week - Sept-Oct 2022
```{r fig1, fig.height=8, fig.width=20}
png("C:/Users/julia/OneDrive/Documents/Morven/Diurnal Cycles/Plots/Radiation.diurnal.fall2022.png",width=800,height=400)

# remove A,c,D
Radiation<-fall2022[ , c("Date","B.rad","E.rad","F.rad","G.rad","N.rad")]

Rad.hourly.means<-Radiation%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  mutate(Day=as.Date(Date))%>%
  mutate(Hour=format(as.POSIXct(Date),format="%H"))%>%
  group_by(Hour)%>%
  mutate(SD = sd(na.omit(unlist(select(cur_data(), 2:6)))))%>%
  mutate(Mean= mean(na.omit(unlist(select(cur_data(), 2:6)))))%>%
  summarise_if(is.numeric, mean)

Rad.hourly.means.long<-Rad.hourly.means%>%
  pivot_longer(cols=c("B.rad","E.rad","F.rad","G.rad","N.rad","Mean"),names_to="Sensor",values_to="value")

ggplot()+
  geom_line(data=Rad.hourly.means,aes(x=Hour,y=Mean,group=1),color="darkgrey",size=2)+
  geom_point(data=Rad.hourly.means.long,aes(x=Hour,y=value,color=Sensor))+
  geom_line(data=Rad.hourly.means.long,aes(x=Hour,y=value,color=Sensor,group=Sensor))+
  labs(title="ARC 1 Mean Hourly Air Temperature (F) Sept 1 - Nov 31, 2022",x="24 Hour Cycle",y="Air Temperature (deg F)", subtitle="F goes down 2022-09-26 21:00")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B.rad"="gold1","C.rad"="red","D.rad"="darkorchid3","E.rad"="navy","F.rad"="maroon","G.rad"="limegreen","N.rad"="darkgreen"))+
  theme1

dev.off()
```


### Radiation by hour over a week - Oct 17-24 2022
```{r fig1, fig.height=8, fig.width=20}
png("C:/Users/julia/OneDrive/Documents/Morven/Diurnal Cycles/Plots/Radiation.diurnal.Oct17_24_2022.png",width=800,height=400)

# remove A,c,D
Radiation<-fall2022[ , c("Date","B.rad","E.rad","F.rad","G.rad","N.rad")]%>%
   filter(Date > "2022-10-17 00:00:00" & Date <"2022-10-24 23:55:00")

Rad.hourly.means<-Radiation%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  mutate(Day=as.Date(Date))%>%
  mutate(Hour=format(as.POSIXct(Date),format="%H"))%>%
  group_by(Hour)%>%
  mutate(SD = sd(na.omit(unlist(select(cur_data(), 2:6)))))%>%
  mutate(Mean= mean(na.omit(unlist(select(cur_data(), 2:6)))))%>%
  summarise_if(is.numeric, mean)

Rad.hourly.means.long<-Rad.hourly.means%>%
  pivot_longer(cols=c("B.rad","E.rad","F.rad","G.rad","N.rad","Mean"),names_to="Sensor",values_to="value")

ggplot()+
  geom_line(data=Rad.hourly.means,aes(x=Hour,y=Mean,group=1),color="darkgrey",size=2)+
  geom_point(data=Rad.hourly.means.long,aes(x=Hour,y=value,color=Sensor))+
  geom_line(data=Rad.hourly.means.long,aes(x=Hour,y=value,color=Sensor,group=Sensor))+
  labs(title="ARC 1 Mean Hourly Air Temperature (F) October 17-24, 2022",x="24 Hour Cycle",y="Air Temperature (deg F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B.rad"="gold1","C.rad"="red","D.rad"="darkorchid3","E.rad"="navy","F.rad"="maroon","G.rad"="limegreen","N.rad"="darkgreen"))+
  theme1

dev.off()
```




Airtemp Hourly Means 6/19/2022 - 6/24/2022
```{r}
Airtemp<-fall2022[ , c("Date","A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp")]


Airtemp.hourly.means<-Airtemp%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  group_by(Date) %>%
  summarise_if(is.numeric, mean)

Airtemp.hourly.sd<-Airtemp%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  group_by(Date) %>%
  mutate(SD = sd(na.omit(unlist(select(cur_data(), 1:8)))))%>%
  mutate(Mean= mean(na.omit(unlist(select(cur_data(), 1:8)))))%>%
  summarise_if(is.numeric, mean)

datebreaks<-seq.POSIXt(as.POSIXct("2022-09-01 00:00:00"),as.POSIXct("2022-11-30 23:00:00"),by="12 hours")

Airtemp.hourly.means<-melt(Airtemp.hourly.means,id.vars="Date",variable.name="Sensor")

ggplot()+
  geom_line(data=Airtemp.hourly.means, aes(Date,value,group=Sensor),color="gray")+
  geom_point(data=Airtemp.hourly.means, aes(Date,value,group=Sensor),color="gray")+
  geom_errorbar(data=Airtemp.hourly.sd, aes(x=Date,ymin=Mean-SD, ymax=Mean+SD),  position=position_dodge(.9))+
  geom_point(data=Airtemp.hourly.sd, aes(x=Date,y=Mean))+
  scale_x_datetime(breaks=datebreaks)+
  xlim(as.POSIXct("2022-09-01 00:00:00"),as.POSIXct("2022-11-30 23:00:00"))+
  labs(title="ARC 1 Hourly Air Temperature (F) Sept-Nov 2022",x="Date",y="Air Temperature (deg F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  theme_xangle

```




Radiation Hourly Means 6/19/2022 - 6/24/2022
```{r}
Radiation<-fall2022[ , c("Date","B.rad","D.rad","E.rad","F.rad","G.rad","N.rad")]%>%
  replace_with_na(replace=list(D.rad=-888.88))


Radiation.hourly.means<-Radiation%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  group_by(Date) %>%
  summarise_if(is.numeric, mean)

Radiation.hourly.sd<-Radiation%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  group_by(Date) %>%
  mutate(SD = sd(na.omit(unlist(select(cur_data(), 1:6)))))%>%
  mutate(Mean= mean(na.omit(unlist(select(cur_data(), 1:6)))))%>%
  summarise_if(is.numeric, mean)

datebreaks<-seq.POSIXt(as.POSIXct("2022-09-01 00:00:00"),as.POSIXct("2022-11-30 23:00:00"),by="12 hours")

Radiation.hourly.means<-melt(Radiation.hourly.means,id.vars="Date",variable.name="Sensor")

ggplot()+
  geom_line(data=Radiation.hourly.means, aes(Date,value,group=Sensor),color="gray")+
  geom_point(data=Radiation.hourly.means, aes(Date,value,group=Sensor),color="gray")+
  geom_errorbar(data=Radiation.hourly.sd, aes(x=Date,ymin=Mean-SD, ymax=Mean+SD),  position=position_dodge(.9))+
  geom_point(data=Radiation.hourly.sd, aes(x=Date,y=Mean))+
  scale_x_datetime(breaks=datebreaks)+
  xlim(as.POSIXct("2022-09-01 00:00:00"),as.POSIXct("2022-11-30 23:00:00"))+
  labs(title="ARC 1 Hourly Solar Radiation (W/m^2) Sept-Nov 2022",x="Date",y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  theme_xangle

```




Airtemp Hourly Means 6/19/2022 - 6/24/2022
```{r fig1, fig.height=8, fig.width=20}
png("C:/Users/julia/OneDrive/Documents/Morven/Summer 2022/plots/Airtemp.hourly.png",width=800,height=400)

Airtemp<-summer2022[ , c("Date","A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp")]


Airtemp.hourly.means<-Airtemp%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  group_by(Date) %>%
  summarise_if(is.numeric, mean)

Airtemp.hourly.sd<-Airtemp%>%
  mutate(Date=as.POSIXct(cut(Date,breaks="hour")))%>%
  group_by(Date) %>%
  mutate(SD = sd(na.omit(unlist(select(cur_data(), 1:8)))))%>%
  mutate(Mean= mean(na.omit(unlist(select(cur_data(), 1:8)))))%>%
  summarise_if(is.numeric, mean)

datebreaks<-seq.POSIXt(as.POSIXct("2022-06-19 00:00:00"),as.POSIXct("2022-06-24 23:00:00"),by="12 hours")

Airtemp.hourly.means<-melt(Airtemp.hourly.means,id.vars="Date",variable.name="Sensor")

ggplot()+
  geom_line(data=Airtemp.hourly.means, aes(Date,value,color=Sensor))+
  geom_point(data=Airtemp.hourly.means, aes(Date,value,color=Sensor))+
  #geom_point(data=Airtemp.hourly.sd, aes(x=Date,y=Mean))+
  geom_line(data=Airtemp.hourly.sd, aes(x=Date,y=Mean,color="black"),size=2)+
  #geom_errorbar(data=Airtemp.hourly.sd, aes(x=Date,ymin=Mean-SD, ymax=Mean+SD),  position=position_dodge(.9))+
  scale_x_datetime(breaks=datebreaks)+
  xlim(as.POSIXct("2022-07-04 00:00:00"),as.POSIXct("2022-07-04 23:00:00"))+
  labs(title="ARC 1 Hourly Air Temperature (F) July 4, 2022",x="Date",y="Air Temperature (deg F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("A.airtemp"="tan4","B.airtemp"="gold1","C.airtemp"="red","D.airtemp"="darkorchid3","E.airtemp"="navy","F.airtemp"="maroon","G.airtemp"="limegreen","N.airtemp"="darkgreen"))+
  theme_bw()

dev.off()
```

