---
title: "XY Plots Dinural Cycles"
author: "Juliana Cerny"
date: '2023-03-27'
output: html_document
---

# use summer2022.csv, fall2022.csv

load data, change variable names, clean data, set up plot themes 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
library(tidyr)
library(reshape2)
library(lubridate)
library(ggpubr)
library(RColorBrewer)
library(naniar)
library(ggpmisc) # https://cran.r-project.org/web/packages/ggpmisc/index.html 


summer2022<-read.csv("C:/Users/julia/OneDrive/Documents/Morven/Diurnal Cycles/summer2022.csv")

summer2022<-rename(summer2022,
                   A.airtemp="Temperature..RXW.THC.20778368.20779618.1....F..UVA.ARC.1",
                   A.windspeed= "Wind.Speed..RXW.WCF.20778368.20735930.1...mph..UVA.ARC.1",
                   A.winddirection="Wind.Direction..RXW.WCF.20778368.20735930.3......UVA.ARC.1",
                   B.soilmoist="Water.Content..S.SMC.20778368.20773519.1...m.3.m.3..UVA.ARC.1",
                   B.soiltemp="Temperature..S.TMB.20778368.20770097.1....F..UVA.ARC.1",
                   B.airtemp="Temperature..S.THB.20778368.20777744.1....F..UVA.ARC.1",
                   B.rad="Solar.Radiation..S.LIB.20778368.20779676.1...W.m.2..UVA.ARC.1",
                   B.windspeed="Wind.Speed..S.WSB.20778368.20779920.1...mph..UVA.ARC.1",
                   B.winddirection="Wind.Direction..S.WDA.20778368.20774023.1......UVA.ARC.1",
                   C.airtemp="Temperature..RXW.THC.20778368.20780856.1....F..UVA.ARC.1",
                   C.windspeed="Wind.Speed..RXW.WCF.20778368.20735931.1...mph..UVA.ARC.1",
                   C.winddirection="Wind.Direction..RXW.WCF.20778368.20735931.3......UVA.ARC.1",
                   D.airtemp="Temperature..RXW.THC.20778368.20778336.1....F..UVA.ARC.1",
                   D.windspeed="Wind.Speed..RXW.WCF.20778368.20779630.1...mph..UVA.ARC.1",
                   D.winddirection="Wind.Direction..RXW.WCF.20778368.20779630.3......UVA.ARC.1",
                   D.rad="Solar.Radiation..RXW.LIB.20778368.20735864.1...W.m.2..UVA.ARC.1.SR_E6",
                   F.airtemp="Temperature..RXW.THC.20778368.20778338.1....F..UVA.ARC.1",
                   E.soiltemp="Temperature..RXW.TMB.20778368.20776843.1....F..UVA.ARC.1",
                   E.airtemp="Temperature..RXW.THC.20778368.20780852.1....F..UVA.ARC.1",
                   E.rad="Solar.Radiation..RXW.LIB.20778368.20748041.1...W.m.2..UVA.ARC.1.SR_G6",
                   E.windspeed="Wind.Speed..RXW.WCF.20778368.20779625.1...mph..UVA.ARC.1",
                   E.winddirection="Wind.Direction..RXW.WCF.20778368.20779625.3......UVA.ARC.1",
                   F.windspeed="Wind.Speed..RXW.WCF.20778368.20779627.1...mph..UVA.ARC.1",
                   F.winddirection="Wind.Direction..RXW.WCF.20778368.20779627.3......UVA.ARC.1",
                   F.rad="Solar.Radiation..RXW.LIB.20778368.20779612.1...W.m.2..UVA.ARC.1",
                   G.airtemp="Temperature..RXW.THC.20778368.20779619.1....F..UVA.ARC.1",
                   G.windspeed="Wind.Speed..RXW.WCF.20778368.20779626.1...mph..UVA.ARC.1",
                   G.winddirection="Wind.Direction..RXW.WCF.20778368.20779626.3......UVA.ARC.1",
                   G.rad="Solar.Radiation..RXW.LIB.20778368.20735865.1...W.m.2..UVA.ARC.1.SR_G5",
                   N.airtemp="Temperature..RXW.THC.20778368.20780854.1....F..UVA.ARC.1",
                   N.windspeed="Wind.Speed..RXW.WCF.20778368.20779624.1...mph..UVA.ARC.1",
                   N.winddirection="Wind.Direction..RXW.WCF.20778368.20779624.3......UVA.ARC.1",
                   N.rad="Solar.Radiation..RXW.LIB.20778368.20735863.1...W.m.2..UVA.ARC.1.SR_B4")



# converting all variables to numeric and removing commas from radiation vectors

summer2022$Date<-as.POSIXct(summer2022$Date,format="%m/%d/%Y %H",tz="UTC")

summer2022$B.rad<-as.numeric(gsub(",","",summer2022$B.rad))
summer2022$D.rad<-as.numeric(gsub(",","",summer2022$D.rad))
summer2022$E.rad<-as.numeric(gsub(",","",summer2022$E.rad))
summer2022$F.rad<-as.numeric(gsub(",","",summer2022$F.rad))
summer2022$G.rad<-as.numeric(gsub(",","",summer2022$G.rad))
summer2022$N.rad<-as.numeric(gsub(",","",summer2022$N.rad))

summer2022$B.rad<-as.numeric(summer2022$B.rad)
summer2022$D.rad<-as.numeric(summer2022$D.rad)
summer2022$E.rad<-as.numeric(summer2022$E.rad)
summer2022$F.rad<-as.numeric(summer2022$F.rad)
summer2022$G.rad<-as.numeric(summer2022$G.rad)
summer2022$N.rad<-as.numeric(summer2022$N.rad)

#plot theme
theme_xangle<-theme_bw() + 
  theme(title = element_text(size=20),
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust=1))

theme1<-theme_bw()+
  theme(title = element_text(size=20),
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        axis.text.x = element_text( vjust = 1, hjust=1))
```

wideframe to longframe data with just airtemp and radiation, 
new column to label just by Sensor letter
```{r}
# grouped by hour
summer2022$Date<-as.POSIXct(summer2022$Date,format="%m/%d/%Y %H",tz="UTC")

# grouped by day
summer2022daily<-summer2022%>%
  mutate(Date=as.POSIXct(Date,format="%m/%d/%Y",tz="UTC"))

Airtemp<-summer2022[ , c("Date","A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp")]%>%
  group_by(Date)%>%
  summarise(across(c("A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp"), mean), .groups = 'drop') # mean of all measurements within each hour

Airtemp.long<-Airtemp%>%
  pivot_longer(cols=c("A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp"),names_to="Sensor",values_to="Airtemp")%>%
  mutate(Sensor=substr(Sensor,1L,1L)) # extract only letter of Sensor

Radiation<-summer2022[ , c("Date","B.rad","D.rad","E.rad","F.rad","G.rad","N.rad")]%>%
  replace_with_na(replace=list(D.rad=-888.88))%>%
  group_by(Date)%>%
  summarise(across(c("B.rad","D.rad","E.rad","F.rad","G.rad","N.rad"), mean), .groups = 'drop') # mean of all measurements within each hour

Radiation.long<-Radiation%>%
  pivot_longer(cols=c("B.rad","D.rad","E.rad","F.rad","G.rad","N.rad"),names_to="Sensor",values_to="Radiation")%>%
  mutate(Sensor=substr(Sensor,1L,1L))

Soiltemp<-summer2022[ , c("Date","B.soiltemp","E.soiltemp")]%>%
  group_by(Date)%>%
  summarise(across(c("B.soiltemp","E.soiltemp"), mean), .groups = 'drop')

Soiltemp.long<-Soiltemp%>%
  pivot_longer(cols=c("B.soiltemp","E.soiltemp"),names_to="Sensor",values_to="Soiltemp")%>%
  mutate(Sensor=substr(Sensor,1L,1L))

Rad.Airtemp<-inner_join(Airtemp.long,Radiation.long,by=c("Date"="Date","Sensor"="Sensor"))

Soiltemp.Rad.Airtemp<-inner_join(Soiltemp.long,Rad.Airtemp,by=c("Date"="Date","Sensor"="Sensor"))

```

### Summer 

Radiation vs air temp
```{r}

# locally weighted least squares regression (loess)
ggplot(Rad.Airtemp,aes(x=Airtemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  geom_smooth(method = "loess", size=2)+
  labs(title="Solar Radiation vs Air Temp LOESS June 1 - Aug 31, 2022", 
       x= "Air Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1


## gppmisc to add labels of regression line equation and R2
# linear
  ggplot(Rad.Airtemp,aes(x=Airtemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(size=2) +
  stat_poly_eq(aes(label = paste(after_stat(eq.label),after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Solar Radiation vs Air Temp Linear Model, June 1 - Aug 31, 2022", 
       x= "Air Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1
  
# quadratic
ggplot(Rad.Airtemp,aes(x=Airtemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(formula = y ~ poly(x, 2, raw = TRUE),size=2) +
  stat_poly_eq(formula = y ~ poly(x, 2, raw = TRUE),aes(label = paste(after_stat(eq.label),
                                                                      after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Solar Radiation vs Air Temp Quadratic Model, June 1 - Aug 31, 2022", 
       x= "Air Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1

# cubic
ggplot(Rad.Airtemp,aes(x=Airtemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(formula = y ~ poly(x, 3, raw = TRUE),size=2) +
  stat_poly_eq(formula = y ~ poly(x, 3, raw = TRUE),aes(label = paste(after_stat(eq.label),
                                                                      after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Solar Radiation vs Air Temp Cubic Model, June 1 - Aug 31, 2022", 
       x= "Air Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1
```
<https://stackoverflow.com/questions/7549694/add-regression-line-equation-and-r2-on-graph>


Soil temp vs air temp
```{r}
# locally weighted least squares regression (loess)
ggplot(Soiltemp.Rad.Airtemp,aes(x=Airtemp,y=Soiltemp,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  geom_smooth(method = "loess", size=2)+
  labs(title="Soil Temp vs Air Temp LOESS June 1 - Aug 31, 2022", 
       x= "Air Temperature (F)", y="Soil Temperatre (F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1


## gppmisc to add labels of regression line equation and R2
# linear
  ggplot(Soiltemp.Rad.Airtemp,aes(x=Airtemp,y=Soiltemp,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(size=2) +
  stat_poly_eq(aes(label = paste(after_stat(eq.label),after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Soil Temp vs Air Temp Linear Model, June 1 - Aug 31, 2022", 
       x= "Air Temperature (F)", y="Soil Temperatre (F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1
  
# Quadratic
 ggplot(Soiltemp.Rad.Airtemp,aes(x=Airtemp,y=Soiltemp,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(formula = y ~ poly(x, 2, raw = TRUE),size=2) +
  stat_poly_eq(formula = y ~ poly(x, 2, raw = TRUE),aes(label = paste(after_stat(eq.label),
                                                                      after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Soil Temp vs Air Temp Quadratic Model, June 1 - Aug 31, 2022", 
       x= "Air Temperature (F)", y="Soil Temperatre (F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1

# Cubic
 ggplot(Soiltemp.Rad.Airtemp,aes(x=Airtemp,y=Soiltemp,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(formula = y ~ poly(x, 3, raw = TRUE),size=2) +
  stat_poly_eq(formula = y ~ poly(x, 3, raw = TRUE),aes(label = paste(after_stat(eq.label),
                                                                      after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Soil Temp vs Air Temp Cubic Model, June 1 - Aug 31, 2022", 
       x= "Air Temperature (F)", y="Soil Temperatre (F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1
```


# Soil temp vs radiation
```{r}

# locally weighted least squares regression (loess)
ggplot(Soiltemp.Rad.Airtemp,aes(x=Soiltemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  geom_smooth(method = "loess", size=2)+
  labs(title="Soiltemp vs Radiation LOESS June 1 - Aug 31, 2022", 
       x= "Soil Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1


## gppmisc to add labels of regression line equation and R2
# linear
ggplot(Soiltemp.Rad.Airtemp,aes(x=Soiltemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(size=2) +
  stat_poly_eq(aes(label = paste(after_stat(eq.label),after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Soiltemp vs Radiation Linear Model, June 1 - Aug 31, 2022", 
       x= "Soil Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1
  
# Quadratic
ggplot(Soiltemp.Rad.Airtemp,aes(x=Soiltemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(formula = y ~ poly(x, 2, raw = TRUE),size=2) +
  stat_poly_eq(formula = y ~ poly(x, 2, raw = TRUE),aes(label = paste(after_stat(eq.label),
                                                                      after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Soiltemp vs Radiation Quadratic Model, June 1 - Aug 31, 2022", 
       x= "Soil Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1

# Cubic
ggplot(Soiltemp.Rad.Airtemp,aes(x=Soiltemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(formula = y ~ poly(x, 3, raw = TRUE),size=2) +
  stat_poly_eq(formula = y ~ poly(x, 3, raw = TRUE),aes(label = paste(after_stat(eq.label),
                                                                      after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Soiltemp vs Radiation Cubic Model, June 1 - Aug 31, 2022", 
       x= "Soil Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1
```


########################################################################################
########################################################################################

### Fall Data
```{r}

fall2022<-read.csv("C:/Users/julia/OneDrive/Documents/Morven/Diurnal Cycles/fall2022.csv")

fall2022<-rename(fall2022,
                   A.airtemp="Temperature..RXW.THC.20778368.20779618.1....F..UVA.ARC.1",
                   B.airtemp="Temperature..S.THB.20778368.20777744.1....F..UVA.ARC.1",
                   B.soiltemp="Temperature..S.TMB.20778368.20770097.1....F..UVA.ARC.1",
                   B.rad="Solar.Radiation..S.LIB.20778368.20779676.1...W.m.2..UVA.ARC.1",
                   C.airtemp="Temperature..RXW.THC.20778368.20780856.1....F..UVA.ARC.1",
                   D.airtemp="Temperature..RXW.THC.20778368.20778336.1....F..UVA.ARC.1",
                   D.rad="Solar.Radiation..RXW.LIB.20778368.20735864.1...W.m.2..UVA.ARC.1.SR_E6",
                   F.airtemp="Temperature..RXW.THC.20778368.20778338.1....F..UVA.ARC.1",
                   E.airtemp="Temperature..RXW.THC.20778368.20780852.1....F..UVA.ARC.1",
                   E.rad="Solar.Radiation..RXW.LIB.20778368.20748041.1...W.m.2..UVA.ARC.1.SR_G6",
                   E.soiltemp="Temperature..RXW.TMB.20778368.20776843.1....F..UVA.ARC.1",
                   F.rad="Solar.Radiation..RXW.LIB.20778368.20779612.1...W.m.2..UVA.ARC.1",
                   G.airtemp="Temperature..RXW.THC.20778368.20779619.1....F..UVA.ARC.1",
                   G.rad="Solar.Radiation..RXW.LIB.20778368.20735865.1...W.m.2..UVA.ARC.1.SR_G5",
                   N.airtemp="Temperature..RXW.THC.20778368.20780854.1....F..UVA.ARC.1",
                   N.rad="Solar.Radiation..RXW.LIB.20778368.20735863.1...W.m.2..UVA.ARC.1.SR_B4")
```



converting all variables to numeric and removing commas from radiation vectors
```{r}
fall2022$Date<-as.POSIXct(fall2022$Date,format="%m/%d/%Y %H",tz="UTC")

fall2022$B.rad<-as.numeric(gsub(",","",fall2022$B.rad))
fall2022$D.rad<-as.numeric(gsub(",","",fall2022$D.rad))
fall2022$E.rad<-as.numeric(gsub(",","",fall2022$E.rad))
fall2022$F.rad<-as.numeric(gsub(",","",fall2022$F.rad))
fall2022$G.rad<-as.numeric(gsub(",","",fall2022$G.rad))
fall2022$N.rad<-as.numeric(gsub(",","",fall2022$N.rad))

fall2022$B.rad<-as.numeric(fall2022$B.rad)
fall2022$D.rad<-as.numeric(fall2022$D.rad)
fall2022$E.rad<-as.numeric(fall2022$E.rad)
fall2022$F.rad<-as.numeric(fall2022$F.rad)
fall2022$G.rad<-as.numeric(fall2022$G.rad)
fall2022$N.rad<-as.numeric(fall2022$N.rad)
```


separate variables into new dataframes
```{r}
# grouped by hour
fall2022$Date<-as.POSIXct(fall2022$Date,format="%m/%d/%Y %H",tz="UTC")

# grouped by day
fall2022daily<-fall2022%>%
  mutate(Date=as.POSIXct(Date,format="%m/%d/%Y",tz="UTC"))

Airtemp<-fall2022[ , c("Date","A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp")]%>%
  group_by(Date)%>%
  summarise(across(c("A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp"), mean), .groups = 'drop') # mean of all measurements within each hour

Airtemp.long<-Airtemp%>%
  pivot_longer(cols=c("A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp"),names_to="Sensor",values_to="Airtemp")%>%
  mutate(Sensor=substr(Sensor,1L,1L)) # extract only letter of Sensor

Radiation<-fall2022[ , c("Date","B.rad","E.rad","F.rad","G.rad","N.rad")]%>%
  group_by(Date)%>%
  summarise(across(c("B.rad","E.rad","F.rad","G.rad","N.rad"), mean), .groups = 'drop') # mean of all measurements within each hour

Radiation.long<-Radiation%>%
  pivot_longer(cols=c("B.rad","E.rad","F.rad","G.rad","N.rad"),names_to="Sensor",values_to="Radiation")%>%
  mutate(Sensor=substr(Sensor,1L,1L))

Soiltemp<-fall2022[ , c("Date","B.soiltemp","E.soiltemp")]%>%
  group_by(Date)%>%
  summarise(across(c("B.soiltemp","E.soiltemp"), mean), .groups = 'drop')

Soiltemp.long<-Soiltemp%>%
  pivot_longer(cols=c("B.soiltemp","E.soiltemp"),names_to="Sensor",values_to="Soiltemp")%>%
  mutate(Sensor=substr(Sensor,1L,1L))

Rad.Airtemp<-inner_join(Airtemp.long,Radiation.long,by=c("Date"="Date","Sensor"="Sensor"))

Soiltemp.Rad.Airtemp<-inner_join(Soiltemp.long,Rad.Airtemp,by=c("Date"="Date","Sensor"="Sensor"))
```


Airtemp vs radiation
```{r}
# locally weighted least squares regression (loess)
ggplot(Rad.Airtemp,aes(x=Airtemp,y=Radiation,color=Sensor,fill=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  geom_smooth(method = "loess", size=2)+
  labs(title="Solar Radiation vs Air Temp LOESS Sept 1 - Nov 31, 2022", 
       x= "Air Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  scale_fill_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1


## gppmisc to add labels of regression line equation and R2
# linear
  ggplot(Rad.Airtemp,aes(x=Airtemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(size=2) +
  stat_poly_eq(aes(label = paste(after_stat(eq.label),after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Solar Radiation vs Air Temp Linear Model, Sept 1 - Nov 31, 2022", 
       x= "Air Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1
  
# Quadratic
ggplot(Rad.Airtemp,aes(x=Airtemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(formula = y ~ poly(x, 2, raw = TRUE),size=2) +
  stat_poly_eq(formula = y ~ poly(x, 2, raw = TRUE),aes(label = paste(after_stat(eq.label),
                                                                      after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Solar Radiation vs Air Temp Quadratic Model, Sept 1 - Nov 31, 2022", 
       x= "Air Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1

# Cubic
ggplot(Rad.Airtemp,aes(x=Airtemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(formula = y ~ poly(x, 3, raw = TRUE),size=2) +
  stat_poly_eq(formula = y ~ poly(x, 3, raw = TRUE),aes(label = paste(after_stat(eq.label),
                                                                      after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Solar Radiation vs Air Temp Cubic Model, Sept 1 - Nov 31, 2022", 
       x= "Air Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1
```

# Soil temp vs air temp
```{r}

# locally weighted least squares regression (loess)
ggplot(Soiltemp.Rad.Airtemp,aes(x=Airtemp,y=Soiltemp,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  geom_smooth(method = "loess", size=2)+
  labs(title="Soil Temp vs Air Temp LOESS Sept 1 - Nov 31, 2022", 
       x= "Air Temperature (F)", y="Soil Temperatre (F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1


## gppmisc to add labels of regression line equation and R2
# linear
  ggplot(Soiltemp.Rad.Airtemp,aes(x=Airtemp,y=Soiltemp,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(size=2) +
  stat_poly_eq(aes(label = paste(after_stat(eq.label),after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Soil Temp vs Air Temp Linear Model, Sept 1 - Nov 31, 2022", 
       x= "Air Temperature (F)", y="Soil Temperatre (F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1
  
# Quadratic
 ggplot(Soiltemp.Rad.Airtemp,aes(x=Airtemp,y=Soiltemp,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(formula = y ~ poly(x, 2, raw = TRUE),size=2) +
  stat_poly_eq(formula = y ~ poly(x, 2, raw = TRUE),aes(label = paste(after_stat(eq.label),
                                                                      after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Soil Temp vs Air Temp Quadratic Model, Sept 1 - Nov 31, 2022", 
       x= "Air Temperature (F)", y="Soil Temperatre (F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1

# Cubic
 ggplot(Soiltemp.Rad.Airtemp,aes(x=Airtemp,y=Soiltemp,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(formula = y ~ poly(x, 3, raw = TRUE),size=2) +
  stat_poly_eq(formula = y ~ poly(x, 3, raw = TRUE),aes(label = paste(after_stat(eq.label),
                                                                      after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Soil Temp vs Air Temp Cubic Model, Sept 1 - Nov 31, 2022", 
       x= "Air Temperature (F)", y="Soil Temperatre (F)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1
```


# Soil temp vs radiation
```{r}

# locally weighted least squares regression (loess)
ggplot(Soiltemp.Rad.Airtemp,aes(x=Soiltemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  geom_smooth(method = "loess", size=2)+
  labs(title="Soiltemp vs Radiation LOESS Sept 1 - Nov 31, 2022", 
       x= "Soil Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1


## gppmisc to add labels of regression line equation and R2
# linear
ggplot(Soiltemp.Rad.Airtemp,aes(x=Soiltemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(size=2) +
  stat_poly_eq(aes(label = paste(after_stat(eq.label),after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Soiltemp vs Radiation Linear Model, Sept 1 - Nov 31, 2022", 
       x= "Soil Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1
  
# Quadratic
ggplot(Soiltemp.Rad.Airtemp,aes(x=Soiltemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(formula = y ~ poly(x, 2, raw = TRUE),size=2) +
  stat_poly_eq(formula = y ~ poly(x, 2, raw = TRUE),aes(label = paste(after_stat(eq.label),
                                                                      after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Soiltemp vs Radiation Quadratic Model, Sept 1 - Nov 31, 2022", 
       x= "Soil Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1

# Cubic
ggplot(Soiltemp.Rad.Airtemp,aes(x=Soiltemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  stat_poly_line(formula = y ~ poly(x, 3, raw = TRUE),size=2) +
  stat_poly_eq(formula = y ~ poly(x, 3, raw = TRUE),aes(label = paste(after_stat(eq.label),
                                                                      after_stat(rr.label), sep = "*\", \"*"))) +
  labs(title="Soiltemp vs Radiation Cubic Model, Sept 1 - Nov 31, 2022", 
       x= "Soil Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1
```



###################################################

Summer - Using every observation (every 5 minutes)
```{r}

Airtemp<-summer2022[ , c("Date","A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp")]

Airtemp.long<-Airtemp%>%
  pivot_longer(cols=c("A.airtemp","B.airtemp","C.airtemp","D.airtemp","E.airtemp","F.airtemp","G.airtemp","N.airtemp"),names_to="Sensor",values_to="Airtemp")%>%
  mutate(Sensor=substr(Sensor,1L,1L)) # extract only letter of Sensor

Radiation<-summer2022[ , c("Date","B.rad","D.rad","E.rad","F.rad","G.rad","N.rad")]%>%
  replace_with_na(replace=list(D.rad=-888.88))

Radiation.long<-Radiation%>%
  pivot_longer(cols=c("B.rad","D.rad","E.rad","F.rad","G.rad","N.rad"),names_to="Sensor",values_to="Radiation")%>%
  mutate(Sensor=substr(Sensor,1L,1L))

Rad.Airtemp<-inner_join(Airtemp.long,Radiation.long,by=c("Date"="Date","Sensor"="Sensor"))

# linear model
ggplot(Rad.Airtemp,aes(x=Airtemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  geom_smooth(method = "lm", se=T, fill = NA, size=2)+
  labs(title="Solar Radiation vs Air Temp Sept 1 - Nov 31, 2022", 
       x= "Air Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1

# locally weighted least squares regression (loess)
ggplot(Rad.Airtemp,aes(x=Airtemp,y=Radiation,color=Sensor,fill=Sensor))+
  geom_line()+
  geom_point()+
  geom_smooth(method = "loess", se=T, fill = NA, size=2)+
  labs(title="Solar Radiation vs Air Temp Sept 1 - Nov 31, 2022", 
       x= "Air Temperature (F)", y="Solar Radiation (W/m^2)")+
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))+
  scale_color_manual(values = c ("B"="gold1","C"="red","D"="darkorchid3","E"="navy","F"="maroon","G"="limegreen","N"="darkgreen"))+
  theme1
 
```
